One more attempt on ArXe

### 2015-03-13 theory.tex
add more theory text

In case of the electronic decay processes one is interested in the
energies of the initial $E_{in}$ and the final states $E_{fin}$ of
the corresponding processes in order to determine, whether a channel $\beta$
is open, i.e., in accordance with energy conservation, or not. When the channel
is open, the excess energy is carried away by the emitted electron $E_{sec}$
in form of its kinetic energy. These energies can in the model
of pairs and triples be approximated to be

\begin{align}
 E_{in}^\beta  &= SIP(X_{in}^\beta) \label{equation:E_in}\\
 E_{fin}^\beta &= SIP(X_{fin1}^\beta) + SIP(X_{fin2}^\beta) + \frac 1d
           \label{equation:E_fin}\\
 E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}
\end{align}
where $X_{in}$ denotes the initially ionized atom and
$X_{fin1}$ and $X_{fin2}$ describe the two ionized
atoms in the final state. $\beta$ denotes the decay channel characterized
by the quantum numbers of the ionized atoms in the pairs
and triples and $d$ denotes the interatomic distance between the atoms
$X_{fin1}$ and $X_{fin2}$. The initially ionized atom $X_{in}$ can
coincide with one or both of
the final state atoms
$X_{fin1}$ and $X_{fin2}$. As explained in
chapter \ref{chapter:autoionization}, the distribution
of the vacancies over the different
atoms determines the kind of electronic decay process at hand. Hence, in an
Auger process all three atoms would coincide, for an ICD $X_{in}$
would coincide with one of $X_{fin1}$ and $X_{fin2}$ and for an {ETMD}3
all ionized states are located on different atoms.

@@

This ad hoc approach easily allows to correct for energetic shifts of         
ionization potentials as observed in larger clusters.

\begin{align}
 \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \Gamma_{ICD,i,\beta}\\
 \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \Gamma_{ETMD,j,\beta}\\
\end{align}

$N_{ICD} = N_{in} \cdot N_{fin} = N_{Ar} \cdot N_{Xe}
 = \sum\limits_i N_{ICD,i}$
$N_{ETMD} = N_{in} \cdot N_{fin} (N_{fin} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
 = \sum\limits_j N_{ETMD,j}$

$N_{ICD,i}$ and $N_{ETMD,j}$ depend on the structure

@@

@@

\begin{equation}
 \Gamma_{ETMD,j,\beta} = 2\pi \sum\limits_{m,M_{in}',D}
                        \frac{a_m \Theta_m(\alpha_i) \sigma^{(X_E)}(\omega_{vp,\beta})
                              \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
                         {R_j^6 \omega_{vp,\beta}}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

\begin{equation}
\end{equation}

>>>>

In order to determine, whether a channel $\beta$ for a given geometry and decay
mechanism is open ,i.e., in accordance with energy conservation,
the energies of the initial $E_{in}$ and the final states $E_{fin}$ of
the corresponding processes are necessary.
When the channel
is open, the excess energy is carried away by the emitted electron $E_{sec}$
in form of its kinetic energy. These energies can in the model
of pairs and triples be approximated to be

\begin{align}
 E_{in}        &= SIP(X_{in}) \label{equation:E_in}\\
 E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
           \label{equation:E_fin}\\
 E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}
\end{align}
where $X_{in}$ denotes the initially ionized atom and
$X_{D}$ and $X_{E}$ describe the electron donating atom and electron
emitting atom, respectively.
$\beta$ denotes the decay channel characterized
by the quantum numbers of the ionized atoms in the pairs
and triples and $d$ denotes the interatomic distance between the atoms
$X_{D}$ and $X_{E}$. The initially ionized atom $X_{in}$ can
coincide with one or both of
the final state atoms
$X_{D}$ and $X_{E}$.
The distribution of the vacancies over the different
atoms determines the kind of electronic decay process at hand. Hence, in an
Auger process all three atoms would coincide, for an ICD $X_{in}$
would coincide with one of $X_{D}$ and $X_{E}$ and for an {ETMD}3
all ionized states are located on different atoms.

@@

This ad hoc approach easily allows to correct for energetic shifts of         
ionization potentials as observed in larger clusters by adding experimentally
or theoretically determined energy shifts $\Delta E(X_{A}^{\beta})$
for a given role in the decay
$A=in,D,E$ and a channel $\beta$ which yields
the working expression for the kinetic energy of the secondary electron

\begin{equation}
 E_{sec}^\beta = SIP(X_{in}) + \Delta E (X_{in})
               - SIP(X_{D}^\beta) - \Delta E (X_{D}^\beta)
               - SIP(X_{E}^\beta) - \Delta E (X_{E}^\beta)
               - \frac 1d .
\end{equation}

The total decay width $\Gamma$ is given by the sum over the decay widths
of all decay mechanisms. In case of the ArXe clusters we only consider
ICD and ETMD:

\begin{equation}
 \Gamma = \Gamma_{ICD} + \Gamma_{ETMD} .
\end{equation}

These are given by the sum over the decay widths of all pairs $i$ for the
ICD and all triples $j$ for the ETMD3, respectively and all channels $\beta$.

\begin{align}
 \Gamma_{ICD}  &= \sum\limits_{i,\beta} N_{ICD,i}  \, \Gamma_{ICD,i,\beta}\\
 \Gamma_{ETMD} &= \sum\limits_{j,\beta} N_{ETMD,j} \, \Gamma_{ETMD,j,\beta}\\
\end{align}
Here, $N_{ICD,i}$ and $N_{ETMD,j}$ denote the number of geometrically
equal pairs and triples in a given cluster structure. The total number of pairs
reads
$N_{ICD} = N_{in} \cdot N_{D/E} = N_{Ar} \cdot N_{Xe}
 = \sum\limits_i N_{ICD,i}$ and the number of triples as
$N_{ETMD} = N_{in} \cdot N_{D/E} (N_{D/E} - 1) = N_{Ar} \cdot N_{Xe} (N_{Xe} - 1)
 = \sum\limits_j N_{ETMD,j}$.
The number of geometrically equal pairs $N_{ICD,i}$ and $N_{ETMD,j}$
strongly depend on the structure of the cluster. From these relationships
it can be seen that a higher xenon content in the cluster statistically
favours the ETMD3 over the ICD.

In previous work \cite{Fasshauer13,Fasshauer_PhD} we have shown that
the decay width for a single pair or triple for a distinct channel $\beta$
following Wentzel \cite{Wentzel27} Feshbach\cite{Feshbach58,Feshbach62}
and Fano \cite{Fano61}

@@

can be approximated by its asymptotic behaviour

@@

\begin{equation}
 \Gamma_{ETMD,j,\beta} = 2\pi \sum\limits_{m,M_{in}',D}
                        \frac{a_m \Theta_m(\alpha_j) \sigma^{(X_E)}(\omega_{vp,\beta})
                              \tilde{D}_{m,j,\beta}(M_{in,D},M_{in,D'})}
                         {R_j^6 \omega_{vp,\beta}}
\end{equation}

depending on constants ($a_m=4,2$) as well as experimental properties
of atoms like ionization cross sections
$\sigma^{(X_E)}(\omega_{vp,\beta})$, radiative lifetimes of the initially
ionized state $\tau_{in,\beta}$ and the excess energy transferred to the
emitting atom (the energy of the virtual photon) $\omega_{vp,\beta}$
and calculated dipole transition moments $\tilde{D}_{m,j,\beta}$, only.
Here, $\Theta_m(\alpha_j)$ is a function depending on the angle $\alpha_j$
of the triple (compare Ref. \cite{Fasshauer13}).
